---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# clevr: Clustering and Link Prediction Evaluation in R

<!-- badges: start -->
<!-- badges: end -->

clevr implements functions for evaluating link prediction and clustering 
algorithms in R. It includes efficient implementations of common performance 
measures, such as:
* pairwise precision, recall, F-measure;
* homogeneity, completeness and V-measure;
* (adjusted) Rand index;
* variation of information; and
* mutual information.
While the current focus is on supervised (a.k.a. external) performance 
measures, unsupervised (internal) measures are also in scope for future 
releases.

## Installation

You can install the latest release from [CRAN](https://CRAN.R-project.org) 
by entering:

``` r
install.packages("clevr")
```

The development version can be installed from GitHub using `devtools`:

``` r
# install.packages("devtools")
devtools::install_github("cleanzr/clevr")
```

## Example

Several functions are included which transform between different clustering 
representations.

```{r example}
library(clevr)
# A clustering of four records represented as a membership vector
pred_membership <- c("Record1" = 1, "Record2" = 1, "Record3" = 1, "Record 4" = 2)

# Represent as a set of record pairs that appear in the same cluster
pred_pairs <- membership_to_pairs(pred_membership)
print(pred_pairs)

# Represent as a list of record clusters
pred_clusters <- membership_to_clusters(pred_membership)
print(pred_clusters)
```

Performance measures are available for evaluating linked pairs:

```{r pair-measures}
true_pairs <- rbind(c("Record1", "Record2"), c("Record3", "Record4"))

pr <- precision_pairs(true_pairs, pred_pairs)
print(pr)

re <- recall_pairs(true_pairs, pred_pairs)
print(re)
```

and for evaluating clusterings:

```{r clust-measures}
true_membership <- c("Record1" = 1, "Record2" = 1, "Record3" = 2, "Record 4" = 2)

ari <- adj_rand_index(true_membership, pred_membership)
print(ari)

vi <- variation_info(true_membership, pred_membership)
print(vi)
```
